APPM report - Draft

### 2022-12-21 paper_version/main.tex
Edited Sections 2 & 3

In summary, we make the following choices \cite[][sec 2.2]{degond_2017}
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}
Assuming this behavior of the dimensionless parameters, the rescaled Euler-Maxwell system
is simplified to a system of PDEs with the dimensionless \emph{Debye length} $\lambda$ as
single parameter, whose value may tend to zero:
\begin{subequations}
  \label{resc}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}+
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{pmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state
$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and
$h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and
electrons,
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons take the form:
\begin{align} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align}
The rescaled material laws (\ref{equ:material_law}) are still given by 
\begin{equation} \label{equ:maxwell_material_law_rescaled}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
\end{equation}
\end{subequations}
with rescaled permittivity $\epsilon$ and permeability $\mu$, however. The
$\lambda$-parameterized rescaled Maxwell-Euler system
(\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) is the
starting point for the development of the numerical method.

@@

The Debye length $\lambda_D$ is the characteristic length over which local net charge is
shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
has a very small value compared to the reference length scale: the typical $\lambda_D$ for
gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which yields the limit model,
formally obtained by setting the rescaled Debye length $\lambda$ to zero in \eqref{resc}:
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0 \tag{\ref{equ:maxwell_faraday_rescaled}},\\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \tag{\ref{equ:maxwell_ampere_rescaled}}\\
        \nabla \cdot \mathbf{B} &= 0, \tag{\ref{equ:maxwell_gauss_B_rescaled}}\\
        \lambda^2 \nabla \cdot \mathbf{D} &= \rho. \tag{\ref{equ:maxwell_gauss_D_rescaled}}
    \end{align*}
\end{minipage}
\hspace{0.6cm}$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
\end{subequations}
\end{minipage}
\end{center}
The quasi-neutral condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of setting $\lambda = 0$ in Gauss's law for the electric field (\ref{equ:maxwell_gauss_D_rescaled}). As in the non-neutral case, Gauss's laws (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of (\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided (\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at initial time.

This limit represents a \emph{singular perturbation problem} in the sense that vanishing $\lambda$ changes the character of the PDE system. To be more specific, for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the quasi-neutral model it responds instantaneously to other quantities according to the constraint (\ref{equ:maxwell_ampere_limit}). We replace (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of (\ref{equ:maxwell_ampere_rescaled}). Meanwhile, due to the link between fluid momenta $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source terms:
\begin{align}
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= \mathbf{S}_1 + \mathbf{S}_2, \label{equ:E}
\end{align}
where
\begin{align*}
    \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_* - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B} - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
\end{align*}
 It is obvious in (\ref{equ:E}) that the electric field propagate with finite speed (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they respond instantaneously everywhere to local excitation (parabolic evolution/elliptic boundary value problems).

@@

We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$ (plamsa domain) and $\Omega_N$ (non-conducting domain). They represent regions of space occupied by plasma and a non-conducting linear dielectric medium (e.g. glass) respectively. We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary with an artificial cut-off boundary. The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding to this setting is sketched in Fig. \ref{fig:domain_sketch} and is the one used in \cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It covers fundamental experimental set-ups, for example, those studying wall-stabilized electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for instance, those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}. 
%\mycomment{Roman: expand on a relevant physical setting, e.g. wall-stabilized arc in hight voltage circuit breakers.}

The Euler equations are defined in $\Omega_P$ with boundary conditions on $\partial\Omega_P$. We consider the physical scenario where plasma is confined by a solid insulator. Therefore, the interface $\Gamma_W$ is treated as reflective wall where fluid particles are bounced back while keeping the tangential velocity and energy unchanged. The contact boundary $\Gamma_C$ is modelled by open boundaries where the plasma and energy can flow through, i.e. ions and electrons are emitted and absorbed by the electrodes.

@@

Maxwell's equations are solved in the whole domain $\Omega$. The insulating boundary $\Gamma_I$ blocks energy interchange and therefore only admits zero electric and magnetic flux, that is, $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and $\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector. We model the electrodes by imposing boundary conditions on the contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$ which is composed of two disjoint connected components. On the contact boundary $\Gamma_C$, the tangential component $\mathbf{E}_t$ of the $\mathbf{E}$-field is vanishing. By Faraday's law (\ref{equ:maxwell_faraday_rescaled}) we have $\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial) boundary $\partial\Omega$, which admits a scalar potential $\varphi$ defined on $\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$ denotes surface gradient. $\varphi$ is constant on $\Gamma_C^+$ and $\Gamma_C^-$. The difference of these two constant values is the voltage drop between the two contacts.

@@

\caption{Sketch of the domain. The right figure shows the cross section in the $x$-$z$ plane.}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \nabla \mathbf{u_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C, \\
    \nabla n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C, \\
    \nabla e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For Maxwell's equations:}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \partial\Omega,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
    \end{align*}
\end{minipage}

@@

\begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel, $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does not support the existence of a surface potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to consider co-homology vector fields \cite{Hiptmair_2021}.
\end{remark}

\subsection{Reformulation} \label{sec:reform_continuous}
In the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}), the Euler system is not defined there due to the absence of plasmas. Consequently, the Maxwell system in $\Omega_N$ boils down to
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}

In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial time. Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.

To see this issue from another perspective, we examine the limit Maxwell system in $\Omega_N$
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_limit}\\ 
    - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins_limit}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_limit}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:gaus_D_ins_limit}.
\end{align}
\end{subequations}

Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant while Gauss's law for the $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer the consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}). However, it is essential for the well-posedness of the problem \cite[][p.  7]{ana_2010}. Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as $\lambda \rightarrow 0$ poses some problem. In other words, the set of equations (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) ``approaches" an ill-posed situation as $\lambda \rightarrow 0$. This is totally fine in the continuous level while it could be problematic on the discrete level due to limited machine precision.

@@

Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that $\psi = 0$ in $\Omega_N$. This is done by taking the divergence of (\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet boundary condition gives vanishing $\psi$. The importance of this reformulation will become clear in the numerical experiments, see Section \ref{sec:numerical_experiment}.

@@

\section{Spatial Discretization} \label{sec:spatial_discretization}
\subsection{Primal-dual Staggered Meshes} \label{sec:mesh-duality}
\subsubsection{Definition and Geometric Construction}
Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use. The spatial domain is covered by two meshes interlacing with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively. The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies inside of a cell of the other mesh} \cite[][Sec. 2]{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered to each other. A simple example for Cartesian meshes is shown in Fig. \ref{fig:cartesian}.

>>>>

In summary, we make the following choices \cite[][sec 2.2]{degond_2017}
\begin{align*}
    \xi \sim g \sim \lambda \in [0,1], \ \ \ \zeta \sim M \sim \eta \sim \beta \sim \mathcal{O}(1).
\end{align*}
Assuming this behavior of the dimensionless parameters, the rescaled Euler-Maxwell system
is simplified to a system of PDEs with the dimensionless \emph{Debye length} $\lambda$ as
single parameter, whose value may tend to zero:
\begin{subequations}
  \label{resc}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \colorbox{yellow!30}{$\displaystyle\lambda^2$} \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \colorbox{yellow!30}{$\displaystyle\lambda^2$} \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}+
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{pmatrix}, \label{equ:euler_rescaled}
\end{align}
with the equation of state
$e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and
$h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and
electrons,
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons take the form:
\begin{align} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align}
The rescaled material laws (\ref{equ:material_law}) are still given by 
\begin{equation} \label{equ:maxwell_material_law_rescaled}
    \mathbf{D} = \epsilon \mathbf{E}, \ \ \ \mathbf{B} = \mu \mathbf{H}, 
\end{equation}
\end{subequations}
with rescaled permittivity $\epsilon$ and permeability $\mu$, however. The
$\lambda$-parameterized rescaled Maxwell-Euler system
(\ref{equ:maxwell_faraday_rescaled})-(\ref{equ:maxwell_material_law_rescaled}) is the
starting point for the development of the numerical method.

@@

The Debye length $\lambda_D$ is the characteristic length over which local net charge is
shielded, see \cite[Sec. 1.4]{chen2016} for the underlying physics. In many situations, it
has a very small value compared to the reference length scale: the typical $\lambda_D$ for
gas discharge and Tokamak fusion reactors is $10^{-4}$ meter, for interstellar medium, the
magnitude is about $1$ meter \cite[Ch. 20]{Blandford_2013}. Then the quasi-neutrality
assumption $\rho = \sum_* q_*n_* \approx 0$ is justified, which is typical of the limit
model.  Formally we obtain it by setting the rescaled Debye length $\lambda$ to zero in
\eqref{resc}:
\begin{center}
    \begin{minipage}{0.3\textwidth}
    \begin{align*}
        \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0 \tag{\ref{equ:maxwell_faraday_rescaled}},\\ 
        \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \tag{\ref{equ:maxwell_ampere_rescaled}}\\
        \nabla \cdot \mathbf{B} &= 0, \tag{\ref{equ:maxwell_gauss_B_rescaled}}\\
        \lambda^2 \nabla \cdot \mathbf{D} &= \rho. \tag{\ref{equ:maxwell_gauss_D_rescaled}}
    \end{align*}
\end{minipage}
\hspace{0.6cm}$\xrightarrow[]{\lambda \rightarrow 0}$
\begin{minipage}{0.3\textwidth}
  \begin{subequations}
    \label{limit}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_limit} \\ 
    - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_limit} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_limit}\\
     0 &= \rho. \label{equ:maxwell_gauss_D_limit}
\end{align}
\end{subequations}
\end{minipage}
\end{center}
The quasi-neutrality condition (\ref{equ:maxwell_gauss_D_limit}) is the consequence of
setting $\lambda = 0$ in Gauss's law for the electric field
(\ref{equ:maxwell_gauss_D_rescaled}). As in the non-neutral case, Gauss's laws
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are the consequence of
(\ref{equ:maxwell_faraday_limit}) (\ref{equ:maxwell_ampere_limit}) provided
(\ref{equ:maxwell_gauss_B_limit}) (\ref{equ:maxwell_gauss_D_limit}) are satisfied at
initial time.

\begin{remark}
  \label{rem:limit}
  The limit \eqref{limit} represents a \emph{singular perturbation problem} in the sense
  that vanishing $\lambda$ changes the character of the PDE system. To be more specific,
  for $\lambda = \mathcal{O}(1)$ the $\mathbf{E}$-field evolves with time whereas in the
  quasi-neutral model it responds instantaneously to other quantities according to the
  constraint (\ref{equ:maxwell_ampere_limit}). We replace
  (\ref{equ:maxwell_ampere_rescaled}) by the sum of the rotation of
  (\ref{equ:maxwell_faraday_rescaled}) and the time-derivative of
  (\ref{equ:maxwell_ampere_rescaled}). Meanwhile, due to the link between fluid momenta
  $n_*u_*$ and current in (\ref{equ:maxwell_euler_coupling}), the term
  $\partial_t\mathbf{J}$ can be reformulated by the momentum equation according to
  (\ref{equ:euler_rescaled}) and we end up with the following wave equation with source
  terms:
  \begin{align}
    \lambda^2\partial_t^2 \mathbf{E} + \nabla \times \nabla \times \mathbf{E} &= \mathbf{S}_1 + \mathbf{S}_2, \label{equ:E}
  \end{align}
  where
  \begin{align}
    \mathbf{S}_1 &= - \left(\sum_*\varepsilon_*^{-2}q_*^2n_*\right)\mathbf{E}, \\
    \mathbf{S}_2 &= \sum_* q_*\nabla\cdot(n_* \mathbf{u}_* \otimes \mathbf{u}_*
    - \varepsilon_*^{-2}p_*\mathbb{I}\varepsilon_*^{-2}q_*^2n_*\mathbf{u}_*\times\mathbf{B}
    - q_*\varepsilon_*^{-2}\mathbf{R}^\text{coll}_*).
  \end{align}
  It is obvious in (\ref{equ:E}) that the electric fields propagate with finite speed
  (hyperbolic evolution) when $\lambda = \mathcal{O}(1)$, whereas for $\lambda = 0$ they
  respond instantaneously everywhere to local excitation (parabolic evolution/elliptic
  boundary value problems).
\end{remark}

@@

We consider a simply-connected domain $\Omega$ comprising two sub-domains $\Omega_P$
(\textbf{p}lasma domain) and $\Omega_N$ (\textbf{n}on-conducting domain). They represent
regions of space occupied by plasma and a non-conducting linear dielectric medium
(e.g. glass) respectively. We use the notation
$\Gamma_C := \partial\Omega \cap \partial\Omega_P$ to denote the contact boundary, and
$\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which is an
``artificial'' cut-off boundary. The interface between the two domains is denoted by
$\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding
to this setting is sketched in Fig. \ref{fig:domain_sketch} and is the one used in
\cite[][Ch. 1, Sec. 4]{fuchs_2021}. This situation is simple, but highly relevant. It
covers fundamental experimental set-ups, for example, those studying wall-stabilized
electric arcs \cite{GGF05}, but is also adequate for a range of industrial plasmas, for
instance, for those occurring in high-voltage circuit breakers \cite{SEE15,MGU20}.

The Euler equations are defined in $\Omega_P$ with boundary conditions on
$\partial\Omega_P$. We consider the physical scenario where the plasma is confined by a
solid insulator. Therefore, the interface $\Gamma_W$ is treated as a reflective wall where
fluid particles are bouncing back while keeping the tangential velocity and energy
unchanged. The contact boundary $\Gamma_C$ is modelled by open boundaries, where charge
carriers and energy can pass through, i.e., ions and electrons are emitted and absorbed by
the electrodes.

@@

Maxwell's equations are posed on the whole domain $\Omega$. The insulating boundary
$\Gamma_I$ blocks energy transfer and therefore only admits zero electric and magnetic
flux, that is, $\mathbf{D}\cdot \mathbf{n}|_{\Gamma_I} = 0$ and
$\mathbf{B} \cdot \mathbf{n}|_{\Gamma_I} = 0$ where $\mathbf{n}$ is the normal vector
\cite{Hiptmair_2021}. We model the electrodes by imposing boundary conditions on the
contact boundary $\Gamma_C = \Gamma_C^+\cup \Gamma_C^-$, which is composed of two disjoint
connected components. On the contact boundary $\Gamma_C$, the tangential component
$\mathbf{E}_t$ of the $\mathbf{E}$-field vanishes. By Faraday's law
(\ref{equ:maxwell_faraday_rescaled}) we have
$\nabla \times \mathbf{E} \cdot \mathbf{n} = 0$ on the whole (topologically trivial)
boundary $\partial\Omega$, which admits a scalar potential $\varphi$ defined on
$\partial\Omega$ such that $\mathbf{E}_t = \nabla_\Gamma \varphi$ where $\nabla_\Gamma$
denotes surface gradient. The scalar potential $\varphi$ is constant on $\Gamma_C^+$ and
$\Gamma_C^-$. The difference of these two constant values gives the voltage drop between the
two contacts.

@@

\caption{The right figure shows the cross section in the $x$-$z$ plane and the different
  parts of the boundary and interfaces.}

@@

\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \nabla \mathbf{u_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C, \\
    \nabla n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C, \\
    \nabla e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W \cup \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For Maxwell's equations:}
    \begin{align*}
    \mathbf{D} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \partial\Omega,  \\
    \mathbf{B} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \varphi = \varphi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm.
    \end{align*}
\end{minipage}

@@

\begin{remark} For a geometric setting with non-trivial topology, e.g. with a tunnel,
  $\nabla \times \mathbf{E}\cdot\mathbf{n} = 0$ does guarantee the existence of a surface
  potential $\varphi$ satisfying $\mathbf{E}_t = \nabla_\Gamma\varphi$. One needs to
  include co-homology vector fields \cite{Hiptmair_2021}.
\end{remark}

\subsection{Stabilization in $\Omega_{N}$}
\label{sec:reform_continuous}

No plasma fills the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}),
and, consequently, the Maxwell system in $\Omega_N$ reduces to 
\begin{subequations}
  \label{eq:mxon}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}
In a non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$
is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are
redundant as long as they are satisfied at initial time. Nonetheless, as the system
approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for the
$\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Schemes based on this set
of PDEs would become unstable as $\lambda \rightarrow 0$. The vanishing divergence
constraint would evaporate as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold
numerically when $\lambda^2$ becomes extremely small.

To view this issue from another perspective, we examine the limit Maxwell system in
$\Omega_N$:
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_limit}\\ 
    - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins_limit}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_limit}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:gaus_D_ins_limit}.
\end{align}
\end{subequations}

Again, Gauss's law for the $\mathbf{B}$-field (\ref{equ:gauss_B_ins_limit}) is redundant,
while Gauss's law for the $\mathbf{D}$-field (\ref{equ:gaus_D_ins_limit}) is no longer a
consequence of Amp\`{e}re's law (\ref{equ:ampere_ins_limit}). However,
\eqref{equ:gaus_D_ins_limit} is essential for the well-posedness of the problem \cite[][p.
7]{ana_2010}. Obviously, the degeneracy of Gauss's law for the $\mathbf{D}$-field in the
system (\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) as
$\lambda \rightarrow 0$ poses some problem. In other words, the set of equations
(\ref{equ:faraday_ins_limit}) to (\ref{equ:gaus_D_ins_limit}) switches to an ill-posed
situation for $\lambda=0$. I computations this will manifest itself as instability 
already for ${\lambda>0}$.

@@

Supplemented with the boundary condition $\psi = 0$ on $\partial\Omega_N$, one can check
that (\ref{equ:faraday_ins_reform}) to (\ref{equ:gauss_D_ins_reform}) are equivalent to
the original formulation (\ref{equ:faraday_ins})-(\ref{equ:gauss_D_ins}) by verifying that
$\psi = 0$ in $\Omega_N$. This is done by taking the divergence of
(\ref{equ:ampere_ins_reform}), which results in $\Delta\psi = 0$ and the zero Dirichlet
boundary condition gives vanishing $\psi$. The importance of this reformulation will
become clear through numerical experiments, see Section \ref{sec:numerical_experiment}.

@@

\section{Spatial Discretization} \label{sec:spatial_discretization}
\subsection{Primal-dual Staggered Meshes} \label{sec:mesh-duality}
\subsubsection{Definition and Geometric Construction}

To prepare the spatial discretization of the Maxwell-Euler system, we introduce
primal-dual staggered meshes, a key component of the discrete exterior calculus (DEC)
discretization of Maxwell's equations. The spatial domain is covered by two meshes
interlacing with each other, denoted by a mesh doublet
$(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively. The
fundamental duality property requires that \emph{each edge of one mesh penetrates a face
  of the other mesh and that each vertex of one mesh lies inside of a cell of the other
  mesh} \cite[][Sec. 2]{weiland_2003}. Examples are shown in Fig.~\ref{fig:cartesian}.
